%\title{LaTeX Example: How to double space a document}
% Based on http://tex.stackexchange.com/questions/50894/how-do-i-double-space-my-abstract-in-latex
\documentclass[12pt]{article}
\usepackage{setspace}   %Allows double spacing with the \doublespacing command
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{lipsum} % Add dummy text
\begin{document}

\begin{titlepage}
	\centering
	{\scshape\LARGE University of Minnesota Duluth \par}
	\vspace{1cm}
	{\scshape\Large \par}
	\vspace{1.5cm}
	{\huge\bfseries Second Writing Assignment: Review on Equifax Data Breach\par}
	\vspace{2cm}
	{\Large\itshape Xinru Yan\par}
	\vspace{2cm}
	{\Large\itshape CS8821 Fall 2017\par}

	\vfill

% Bottom of the page
	{\large \today\par}
\end{titlepage}

\doublespacing

%\section{The Story}
On September 8th, 2017, Equifax announced a cybersecurity incident that affected 143 million consumers in the United States, which has a population of 324 million in 2017 \cite{CI}. According to several reports, the cybercriminals had gained access to personal information including names, dates of birth, addresses, social security numbers and even some driver's license numbers \cite{CI}\cite{WS}. Equifax claimed that it discovered the breach on July 29th, 2017 and the breach could have started as early as mid-May 2017, which means that the company had waited for three months to make it public \cite{YG}.

Equifax, founded in 1899 in Atlanta, Georgia, is one of the three biggest consumer credit reporting agencies (CRAs) which collect information on customers, maintain and report their credit activities \cite{EQX}. 

Many websites have advised people on how to protect themselvs after the breach. For example, you should visit Equifax's website to find out if your information was leaked and enroll in a year of free credit monitoring; you should freeze your credit files, which is free for victims and typically costs ten dollars for non victims, to prevent thieves from doing awful things like opening a new account under your name; you should pay extra attention on your bank accounts and credit cards for any suspicious activities; you should also file your tax as early as you can so that the criminals do not have time to take advantage of it \cite{CI} \cite{AM}. Personally speaking I checked on the website soon after I heard about the breach to see if my information was stolen. I believe these steps are helpful to prevent things from becoming worse. However, even if you follow all these steps perfectly and successfully stop the identity thieves from further harming your credit reports, they still have your private information such as birth date and social security number which can be used against you in a different type of attack.

Bruce Schneier, a computer security professional, wrote an CNN article suggesting that ``We can not rely on the marketplace to regulate the many companies that track our data; Only government action can protect our privacy, and it's badly needed now'' \cite{CNN}. I deeply agree with the idea of ``complaining to your government instead of a specific company that has made mistakes'' since it seems like these companies simply do not take it seriously or seriously enough to protect their customers' private information. Regulations and laws are necessary at this point.  

There was an interesting discussion going on after the security incident which draws attention to the company's Chief Info Security Officer's (CISO) educational background -- she has her BA and MFA in ``Music Composition'' \cite{CE}. According to CNBS, Equifax announced that the CISO will be retiring and replaced \cite{ES}. Some people believe that her non Computer Science (CS) degree is part of the reason why this happened. Some people even believe that ``a woman diversity hire is the reason behind one of the largest hacks of financially sensitive data ever...'' \cite{AC}. I totally disagree with both statements. Gender and major have nothing to do with this breach and are definitely not the real cause. Trying to place the blame onto these details is completely nonsense. People in the CS field come from all kinds of backgrounds. As a matter of fact, educational and gender diversity have played an important role in the field. We should really focus on finding the true cause of the incident and how to fix it.

\newpage
\bibliography{main}
\bibliographystyle{unsrt}

\end{document}